\pkg{cubble}: An R Package for Structuring Spatio-temporal Data

### 2021-11-28 main.Rmd
editing on intro to cubble

---
documentclass: jss
author:
  - name: H. Sherry Zhang
    # department: Department of Econometrics and Business Statistics
    affiliation: Monash University
    #location: Melbourne, Australia
    email: \email{huize.zhang@monash.edu}
  - name: Dianne Cook
    # department: Department of Econometrics and Business Statistics
    affiliation: 'Monash University \AND'
    # location: Melbourne, Australia
    # email:  dicook@monash.edu
  - name: Ursula Laa
    # department: Institute of Statistics
    affiliation: 'University of Natural Resources and Life Sciences \AND'
    # location: Vienna, Austria
    # email:  ursula.laa@boku.ac.at
  - name: Nicolas Langrené
    # department: 34 Village Street, Docklands VIC 3008 Australia
    affiliation: 'CSIRO Data61 \AND'
    # location: Melbourne, Australia
    # email: nicolas.langrene@csiro.au
  - name: Patricia Menéndez
    # department: Department of Econometrics and Business Statistics
    affiliation: 'Monash University \AND'
    # location: Melbourne, Australia
    # email:  patricia.menendez@monash.edu
title:
  formatted: "\\pkg{cubble}: An R Package for Structuring Spatio-temporal Data"
  # If you use tex in the formatted title, alsoge supply version without
  plain:     "cubble: An R Package for Structuring Spatio-temporal Data"
  # For running headers, if needed
  # short:     "\\pkg{foo}: A Capitalized Title"
abstract: >
  The abstract of the article.
keywords:
  # at least one keyword must be supplied
  formatted: [spatio-temporal data,  "\\proglang{R}"]
  plain:     [spatio-temporal data, R]
preamble: >
  \usepackage{amsmath}
output: rticles::jss_article
bibliography: references.bib
---

@@

Currently, available spatio-temporal data structure in R includes: `spacetime`[@spacetime], which proposes four space-time layouts: Full grid (STF), sparse grid(STS), irregular (STI), and trajectory (STT). The data structure it uses is based on `sp` [@sp] and `xts`[@xts], both of which has been replaced by more recent implementations. `spatstat` [@spatstat] implements a `ppp` class for point pattern data; and more recent, `stars` [@stars] implements a spatio-temporal array with the dplyr's data cube structure `cubelyr` [@cubelyr] as its backend. While these implementations either store spatial and temporal variables all in a single table, hence duplicate the spatial variables for each temporal unit; or split them into two separate tables that has the problem of manually joining, mentioned in the previously. None of these packages enjoy both the benefits of being able to separate manipulation in the two dimensions while also keep the data object as a whole. This create a gap in the software development. The requirement for such a tool is important given the ubiquity of spatio-temporal vector data in the wild: the Ireland wind data from `gstat` is an classic example data that splits variables into spatial (`wind.loc`) and temporal (`wind`) dimension;Bureau of Meteorology (BoM) provides climate observations that are widely applied in agriculture and ecology study; air pollution data. \newline

@@

\newpage
# Cubble data structure

## Spatio-temporal data in the wild

Spatio-temporal data don't usually come to the analysts in various forms. Figure \ref{fig:cubble-diagram} groups them into four categories. Despite whichever form the data is in, all the forms have a group identifier, `key`, a time column, `t`, and variables that either various across group, i.e. `lon`, `lat`, $C_s$, or across time, i.e. $V_t$. These identifiers will be the building blocks for the data structure introduced below.

@@

## A new data structure: cubble

A cubble, in essence, wires the spatial and temporal dimension into a single object while provides two forms for manipulation each dimension separately.

In the nest form, Figure \ref{fig:def-cubble}a), a cubble:

  - defines each group in a row,
  - displays the group-related variables in columns, and
  - nests all the time-related variables into a column called `ts`.

In the long form, Figure \ref{fig:def-cubble}b), a cubble:

  - defines the combination of group and timestamp as a row
  - displays time-related variables, along with the group identifier in columns, and
  - stores group-related variables as a attributes called `spatial`.

@@

To create a cubble, you can use `as_cubble` with proper supply of `key`, `index`, and `coords`. [`key` defines whether a variable is spatial or temperal by looking at whether it varies across `key`. For example, `lat` is a spatial variable since for one `id` there's only one `lat` value. `index` and `coords` prescribes the temporal index and spaital coordinates used in the data. These are common variables that should present in the point pattern spatio-temporal data.] The cubble created by default is in the nested form.  \newline

```{r}
(cubble_nested <- climate_flat %>% 
  as_cubble(key = id, index = date, coords = c("long", "lat")))
```

In the `cubble` header, you can read the key variable + number, bbox, and also the name of variable nested in the `ts` column. Here in this example, the temporal variables are precipitation, `prcp`, maximum temporature, `tmax`, and minimum temperature, `tmin`.

In this structure, the nested form is suitable for manipulating the spatial dimension of the data and this would include manipulating variables that 1) are inherently spatial and 2) summarise the temporal variables by `key`. Under the hood, the nested cubble is built on top of the rowwise dataframe (`rowwise_df`). This is design to simplify the code when working with the temporal variables - they are nested into the list-column `ts`.

@@

The verb `stretch()` switch the cubble from the nested form into a long form. Under the hood, it first extracts the spatial variables into a separate tibble to store in the attribute `spatial` and then unnests the `ts` column to show the temporal content:

@@

@@

Building from an underlying `tbl_df` structure, it is natural to implement methods available in `dplyr` to `cubble`. Supported methods in the `cubble` with `dplyr` generics includes: `mutate`, `filter`, `summarise`, `select`, `arrange`, `rename`, `left_join`, `group_by`, `ungroup`, and the slice family (`slice_head`, `slice_tail`, `slice_sample`, `slice_min` and `slice_max`) \textcolor{red}{into a table}.

>>>>

---
documentclass: jss
author:
  - name: H. Sherry Zhang
    # department: Department of Econometrics and Business Statistics
    affiliation: Monash University
    #location: Melbourne, Australia
    email: \email{huize.zhang@monash.edu}
  - name: Dianne Cook
    # department: Department of Econometrics and Business Statistics
    affiliation: 'Monash University \AND'
    # location: Melbourne, Australia
    # email:  dicook@monash.edu
  - name: Ursula Laa
    # department: Institute of Statistics
    affiliation: 'University of Natural Resources and Life Sciences \AND'
    # location: Vienna, Austria
    # email:  ursula.laa@boku.ac.at
  - name: Nicolas Langrené
    # department: 34 Village Street, Docklands VIC 3008 Australia
    affiliation: 'CSIRO Data61 \AND'
    # location: Melbourne, Australia
    # email: nicolas.langrene@csiro.au
  - name: Patricia Menéndez
    # department: Department of Econometrics and Business Statistics
    affiliation: 'Monash University \AND'
    # location: Melbourne, Australia
    # email:  patricia.menendez@monash.edu
title:
  formatted: "\\pkg{cubble}: An R Package for Structuring Spatio-temporal Data"
  # If you use tex in the formatted title, alsoge supply version without
  plain:     "cubble: An R Package for Structuring Spatio-temporal Data"
  # For running headers, if needed
  # short:     "\\pkg{foo}: A Capitalized Title"
abstract: >
  The abstract of the article.
keywords:
  # at least one keyword must be supplied
  formatted: [spatio-temporal data,  "\\proglang{R}"]
  plain:     [spatio-temporal data, R]
preamble: >
  \usepackage{amsmath}
  \usepackage{array}
output: rticles::jss_article
bibliography: references.bib
---

@@

Currently, available spatio-temporal data structure in R includes: `spacetime`[@spacetime], which proposes four space-time layouts: Full grid (STF), sparse grid(STS), irregular (STI), and trajectory (STT). The data structure it uses is based on `sp` [@sp] and `xts`[@xts], both of which has been replaced by more recent implementations. `spatstat` [@spatstat] implements a `ppp` class for point pattern data; and more recent, `stars` [@stars] implements a spatio-temporal array with the dplyr's data cube structure `cubelyr` [@cubelyr] as its backend. While these implementations either store spatial and temporal variables all in a single table, hence duplicate the spatial variables for each temporal unit; or split them into two separate tables that has the problem of manually joining, mentioned in the previously. None of these packages enjoy both the benefits of being able to separate manipulation in the two dimensions while also keep the data object as a whole. This create a gap in the software development. The requirement for such a tool is important given the ubiquity of spatio-temporal vector data in the wild: the Ireland wind data from `gstat` is an classic example data that splits variables into spatial (`wind.loc`) and temporal (`wind`) dimension; Bureau of Meteorology (BoM) provides climate observations that are widely applied in agriculture and ecology study; air pollution data. \newline

@@

\newpage
# The cubble package

Spatio-temporal data usually come in various forms and Figure \ref{fig:cubble-diagram} shows four examples of this. No matter whichever form the data is in, there are always some common components shared by these data. A spatial identifier (`id` in the diagram) identifies each site. The temporal identifier (`t` in the diagram) [...]. Coordinates, comprising of latitude and longitude, are commonly used variables for point pattern data.These identifiers will be the building blocks for the data structure introduced below. For other variables, those invariant at each time stamp are spatial variables and those differ are temporal variables.

@@

In a cubble, there are two forms: 1) nested form, for manipulating the spatial dimension, and 2) long form, for manipulating the temporal dimension. Figure \ref{fig:def-cubble} sketches the two forms along with the associated attributes. A variable identifies by the spatial identifies can come from manipulating spatial variables itself, or summary of temporal variables. The nested cubble is best suited to work with this type of operation, since it defines each spatial unit as a row. The spatial variables are directly displayed in columns. Temporal variables are nested in a column called `ts` and the underlying rowwise dataframe uses a `group` attributes to ensure each row  is in its own group.

<!-- In this structure, the nested form is suitable for manipulating the spatial dimension of the data and this would include manipulating variables that 1) are inherently spatial and 2) summarise the temporal variables by `key`. Under the hood, the nested cubble is built on top of the rowwise dataframe (`rowwise_df`). This is design to simplify the code when working with the temporal variables - they are nested into the list-column `ts`. -->

Temporal operations are suited to be performed in the long cubble as each row is defines as the combination of spatial and temporal identifier. This is also the structure that `tsibble` adopts. Temporal variables are directly displayed. To avoid repeating the same spatial at each temporal unit, all the spatial variables, along with the spatial identifier, are stored as a `spatial` attributes. This information is used when switching back to the nested form.

@@

To use functionalities from cubble, data analysts first need to create a cubble. `as_cubble` create a `cubble` by supplying the three key components: `key` as the spatial identifier; `index` as the temporal identifier; and a vector of `coords` in the order of longitude first and then latitude. The use of `key` and `index` follows the naming convention in `tsibble`. The cubble created by default is in the nested form. Below is an example of creating a cubble:  \newline

```{r}
(cubble_nested <- cubble::climate_flat %>% 
  as_cubble(key = id, index = date, coords = c("long", "lat")))
```

In the `cubble` header, you can read the name of the `key` variable, bbox, and also the name of variable nested in the `ts` column. In this example, the spatial identifier is `id` and the number in the bracket means there are 5 unique `id` in this dataset. The bbox in the second row gives the range of the coordinates. The temporal variables are all nested in the `ts` column, but it could be useful to know the name these variables. The third row in the cubble header shows these names and in this example this includes: precipitation, `prcp`, maximum temporature, `tmax`, and minimum temperature, `tmin`.

@@

From a created cubble in the nested form, analysts may want to directly manipulate the temporal variables. This would require switching to the long form using `stretch()`. The verb `stretch()` switch the cubble from the nested form into a long form. Under the hood, it first extracts the spatial variables into a separate tibble to store in the attribute `spatial` and then unnests the `ts` column to show the temporal content:

@@

## Support on interactive graphics

@@

Building from an underlying `tbl_df` structure, it is natural to implement methods available in `dplyr` to `cubble`. Supported methods in the `cubble` with `dplyr` generics includes:

\begin{center}
\begin{tabular}{ | m{5em} | m{15cm}| } 
\textbf{mutate} \\
\textbf{filter}\\
\textbf{summarise} \\
\textbf{select} \\
\textbf{arrange} \\
\textbf{rename} \\
\textbf{left\_join} \\
\textbf{group\_by} \\
\textbf{ungroup}\\
slice family & \textbf{slice\_head}, \textbf{slice\_tail}, \textbf{slice\_sample}, \textbf{slice\_min} and \textbf{slice\_max} \\
\end{tabular}
\end{center}

### 2021-11-28 main.tex
editing on intro to cubble

\usepackage{amsmath}

@@

Currently, available spatio-temporal data structure in R includes:
\texttt{spacetime}\citep{spacetime}, which proposes four space-time
layouts: Full grid (STF), sparse grid(STS), irregular (STI), and
trajectory (STT). The data structure it uses is based on \texttt{sp}
\citep{sp} and \texttt{xts}\citep{xts}, both of which has been replaced
by more recent implementations. \texttt{spatstat} \citep{spatstat}
implements a \texttt{ppp} class for point pattern data; and more recent,
\texttt{stars} \citep{stars} implements a spatio-temporal array with the
dplyr's data cube structure \texttt{cubelyr} \citep{cubelyr} as its
backend. While these implementations either store spatial and temporal
variables all in a single table, hence duplicate the spatial variables
for each temporal unit; or split them into two separate tables that has
the problem of manually joining, mentioned in the previously. None of
these packages enjoy both the benefits of being able to separate
manipulation in the two dimensions while also keep the data object as a
whole. This create a gap in the software development. The requirement
for such a tool is important given the ubiquity of spatio-temporal
vector data in the wild: the Ireland wind data from \texttt{gstat} is an
classic example data that splits variables into spatial
(\texttt{wind.loc}) and temporal (\texttt{wind}) dimension;Bureau of
Meteorology (BoM) provides climate observations that are widely applied
in agriculture and ecology study; air pollution data. \newline

@@

\hypertarget{cubble-data-structure}{%
\section{Cubble data structure}\label{cubble-data-structure}}

\hypertarget{spatio-temporal-data-in-the-wild}{%
\subsection{Spatio-temporal data in the
wild}\label{spatio-temporal-data-in-the-wild}}

Spatio-temporal data don't usually come to the analysts in various
forms. Figure \ref{fig:cubble-diagram} groups them into four categories.
Despite whichever form the data is in, all the forms have a group
identifier, \texttt{key}, a time column, \texttt{t}, and variables that
either various across group, i.e.~\texttt{lon}, \texttt{lat}, \(C_s\),
or across time, i.e.~\(V_t\). These identifiers will be the building
blocks for the data structure introduced below.

@@

\hypertarget{a-new-data-structure-cubble}{%
\subsection{A new data structure:
cubble}\label{a-new-data-structure-cubble}}

A cubble, in essence, wires the spatial and temporal dimension into a
single object while provides two forms for manipulation each dimension
separately.

In the nest form, Figure \ref{fig:def-cubble}a), a cubble:

\begin{itemize}
\tightlist
\item
  defines each group in a row,
\item
  displays the group-related variables in columns, and
\item
  nests all the time-related variables into a column called \texttt{ts}.
\end{itemize}

In the long form, Figure \ref{fig:def-cubble}b), a cubble:

\begin{itemize}
\tightlist
\item
  defines the combination of group and timestamp as a row
\item
  displays time-related variables, along with the group identifier in
  columns, and
\item
  stores group-related variables as a attributes called
  \texttt{spatial}.
\end{itemize}

@@

To create a cubble, you can use \texttt{as\_cubble} with proper supply
of \texttt{key}, \texttt{index}, and \texttt{coords}. {[}\texttt{key}
defines whether a variable is spatial or temperal by looking at whether
it varies across \texttt{key}. For example, \texttt{lat} is a spatial
variable since for one \texttt{id} there's only one \texttt{lat} value.
\texttt{index} and \texttt{coords} prescribes the temporal index and
spaital coordinates used in the data. These are common variables that
should present in the point pattern spatio-temporal data.{]} The cubble
created by default is in the nested form. \newline

\begin{CodeChunk}
\begin{CodeInput}
R> (cubble_nested <- climate_flat %>% 
+   as_cubble(key = id, index = date, coords = c("long", "lat")))
\end{CodeInput}
\begin{CodeOutput}
# cubble:   id [5]: nested form
# bbox:     [115.97, -32.94, 133.55, -12.42]- check gap on long and lat
# temporal: date [date], prcp [dbl], tmax [dbl], tmin [dbl]
  id            lat  long  elev name           wmo_id ts                
  <chr>       <dbl> <dbl> <dbl> <chr>           <dbl> <list>            
1 ASN00009021 -31.9  116.  15.4 perth airport   94610 <tibble [366 x 4]>
2 ASN00010311 -31.9  117. 179   york            94623 <tibble [366 x 4]>
3 ASN00010614 -32.9  117. 338   narrogin        94627 <tibble [366 x 4]>
4 ASN00014015 -12.4  131.  30.4 darwin airport  94120 <tibble [366 x 4]>
5 ASN00015131 -17.6  134. 220   elliott         94236 <tibble [366 x 4]>
\end{CodeOutput}
\end{CodeChunk}

In the \texttt{cubble} header, you can read the key variable + number,
bbox, and also the name of variable nested in the \texttt{ts} column.
Here in this example, the temporal variables are precipitation,
\texttt{prcp}, maximum temporature, \texttt{tmax}, and minimum
temperature, \texttt{tmin}.

In this structure, the nested form is suitable for manipulating the
spatial dimension of the data and this would include manipulating
variables that 1) are inherently spatial and 2) summarise the temporal
variables by \texttt{key}. Under the hood, the nested cubble is built on
top of the rowwise dataframe (\texttt{rowwise\_df}). This is design to
simplify the code when working with the temporal variables - they are
nested into the list-column \texttt{ts}.

@@

The verb \texttt{stretch()} switch the cubble from the nested form into
a long form. Under the hood, it first extracts the spatial variables
into a separate tibble to store in the attribute \texttt{spatial} and
then unnests the \texttt{ts} column to show the temporal content:

@@

Building from an underlying \texttt{tbl\_df} structure, it is natural to
implement methods available in \texttt{dplyr} to \texttt{cubble}.
Supported methods in the \texttt{cubble} with \texttt{dplyr} generics
includes: \texttt{mutate}, \texttt{filter}, \texttt{summarise},
\texttt{select}, \texttt{arrange}, \texttt{rename}, \texttt{left\_join},
\texttt{group\_by}, \texttt{ungroup}, and the slice family
(\texttt{slice\_head}, \texttt{slice\_tail}, \texttt{slice\_sample},
\texttt{slice\_min} and \texttt{slice\_max})
\textcolor{red}{into a table}.

>>>>

\usepackage{amsmath} \usepackage{array}

@@

Currently, available spatio-temporal data structure in R includes:
\texttt{spacetime}\citep{spacetime}, which proposes four space-time
layouts: Full grid (STF), sparse grid(STS), irregular (STI), and
trajectory (STT). The data structure it uses is based on \texttt{sp}
\citep{sp} and \texttt{xts}\citep{xts}, both of which has been replaced
by more recent implementations. \texttt{spatstat} \citep{spatstat}
implements a \texttt{ppp} class for point pattern data; and more recent,
\texttt{stars} \citep{stars} implements a spatio-temporal array with the
dplyr's data cube structure \texttt{cubelyr} \citep{cubelyr} as its
backend. While these implementations either store spatial and temporal
variables all in a single table, hence duplicate the spatial variables
for each temporal unit; or split them into two separate tables that has
the problem of manually joining, mentioned in the previously. None of
these packages enjoy both the benefits of being able to separate
manipulation in the two dimensions while also keep the data object as a
whole. This create a gap in the software development. The requirement
for such a tool is important given the ubiquity of spatio-temporal
vector data in the wild: the Ireland wind data from \texttt{gstat} is an
classic example data that splits variables into spatial
(\texttt{wind.loc}) and temporal (\texttt{wind}) dimension; Bureau of
Meteorology (BoM) provides climate observations that are widely applied
in agriculture and ecology study; air pollution data. \newline

@@

\hypertarget{the-cubble-package}{%
\section{The cubble package}\label{the-cubble-package}}

Spatio-temporal data usually come in various forms and Figure
\ref{fig:cubble-diagram} shows four examples of this. No matter
whichever form the data is in, there are always some common components
shared by these data. A spatial identifier (\texttt{id} in the diagram)
identifies each site. The temporal identifier (\texttt{t} in the
diagram) {[}\ldots{]}. Coordinates, comprising of latitude and
longitude, are commonly used variables for point pattern data.These
identifiers will be the building blocks for the data structure
introduced below. For other variables, those invariant at each time
stamp are spatial variables and those differ are temporal variables.

@@

In a cubble, there are two forms: 1) nested form, for manipulating the
spatial dimension, and 2) long form, for manipulating the temporal
dimension. Figure \ref{fig:def-cubble} sketches the two forms along with
the associated attributes. A variable identifies by the spatial
identifies can come from manipulating spatial variables itself, or
summary of temporal variables. The nested cubble is best suited to work
with this type of operation, since it defines each spatial unit as a
row. The spatial variables are directly displayed in columns. Temporal
variables are nested in a column called \texttt{ts} and the underlying
rowwise dataframe uses a \texttt{group} attributes to ensure each row is
in its own group.

Temporal operations are suited to be performed in the long cubble as
each row is defines as the combination of spatial and temporal
identifier. This is also the structure that \texttt{tsibble} adopts.
Temporal variables are directly displayed. To avoid repeating the same
spatial at each temporal unit, all the spatial variables, along with the
spatial identifier, are stored as a \texttt{spatial} attributes. This
information is used when switching back to the nested form.

@@

To use functionalities from cubble, data analysts first need to create a
cubble. \texttt{as\_cubble} create a \texttt{cubble} by supplying the
three key components: \texttt{key} as the spatial identifier;
\texttt{index} as the temporal identifier; and a vector of
\texttt{coords} in the order of longitude first and then latitude. The
use of \texttt{key} and \texttt{index} follows the naming convention in
\texttt{tsibble}. The cubble created by default is in the nested form.
Below is an example of creating a cubble: \newline

\begin{CodeChunk}
\begin{CodeInput}
R> (cubble_nested <- cubble::climate_flat %>% 
+   as_cubble(key = id, index = date, coords = c("long", "lat")))
\end{CodeInput}
\begin{CodeOutput}
# cubble:   id [5]: nested form
# bbox:     [115.97, -32.94, 133.55, -12.42]- check gap on long and lat
# temporal: date [date], prcp [dbl], tmax [dbl], tmin [dbl]
  id            lat  long  elev name           wmo_id ts                
  <chr>       <dbl> <dbl> <dbl> <chr>           <dbl> <list>            
1 ASN00009021 -31.9  116.  15.4 perth airport   94610 <tibble [366 x 4]>
2 ASN00010311 -31.9  117. 179   york            94623 <tibble [366 x 4]>
3 ASN00010614 -32.9  117. 338   narrogin        94627 <tibble [366 x 4]>
4 ASN00014015 -12.4  131.  30.4 darwin airport  94120 <tibble [366 x 4]>
5 ASN00015131 -17.6  134. 220   elliott         94236 <tibble [366 x 4]>
\end{CodeOutput}
\end{CodeChunk}

In the \texttt{cubble} header, you can read the name of the \texttt{key}
variable, bbox, and also the name of variable nested in the \texttt{ts}
column. In this example, the spatial identifier is \texttt{id} and the
number in the bracket means there are 5 unique \texttt{id} in this
dataset. The bbox in the second row gives the range of the coordinates.
The temporal variables are all nested in the \texttt{ts} column, but it
could be useful to know the name these variables. The third row in the
cubble header shows these names and in this example this includes:
precipitation, \texttt{prcp}, maximum temporature, \texttt{tmax}, and
minimum temperature, \texttt{tmin}.

@@

From a created cubble in the nested form, analysts may want to directly
manipulate the temporal variables. This would require switching to the
long form using \texttt{stretch()}. The verb \texttt{stretch()} switch
the cubble from the nested form into a long form. Under the hood, it
first extracts the spatial variables into a separate tibble to store in
the attribute \texttt{spatial} and then unnests the \texttt{ts} column
to show the temporal content:

@@

Building from an underlying \texttt{tbl\_df} structure, it is natural to
implement methods available in \texttt{dplyr} to \texttt{cubble}.
Supported methods in the \texttt{cubble} with \texttt{dplyr} generics
includes:

\begin{center}
\begin{tabular}{ | m{5em} | m{15cm}| } 
\textbf{mutate} \\
\textbf{filter}\\
\textbf{summarise} \\
\textbf{select} \\
\textbf{arrange} \\
\textbf{rename} \\
\textbf{left\_join} \\
\textbf{group\_by} \\
\textbf{ungroup}\\
slice family & \textbf{slice\_head}, \textbf{slice\_tail}, \textbf{slice\_sample}, \textbf{slice\_min} and \textbf{slice\_max} \\
\end{tabular}
\end{center}
